\section{Methodology}
\label{sec:methods}

The study aimed to investigate the competitive advantage that can arise for an enterprise
through the adoption of hybrid intelligent systems. Specifically, the study explored the aspect of adaptability
of such hybrid intelligent systems. The study used a mixed-methods approach consisting of a literature
review (secondary data) and qualitative data collection from a focus group of 26 graduate students that 
were selected based on their educational background or work experience in business information systems.

The literature review was conducted to identify factors that contribute to the competitive advantage
of enterprises using AI systems in general, and adaptable hybrid intelligent systems in particular.
The literature search was mainly conducted on Elicit \footnote{\href{https://elicit.org/}{elicit.org}}
and Google Scholar \footnote{\href{https://scholar.google.com/}{scholar.google.com}} using different
query terms, including ``competitive advantage of AI'', ``hybrid intelligent system'',
``expert system'', ``decision support system'', ``human-in-the-loop'', ``competitive advantage and AI'',
etc. Additionally, a forward and backward search was applied on relevant papers that were identified
from the initial literature searches.

The findings from the literature review were used to establish hypotheses on the types of competitive
advantage of adaptable hybrid intelligent systems for enterprises using the example of one industry. Given the
background knowledge of the author, the hypotheses were applied to the scholarly publishing industry.
To test the derived hypotheses, a focus group ($n = 26$) was selected based on their educational
background in business information systems. As part of a workshop the group was split into 4 subgroups and 
each subgroup was presented with one scenario (see Appendix \ref{appendix:scenarios}). The participants were
first introduced to the concepts of hybrid intelligent systems, adaptability of AI, and the competitive advantage
of AI. Then, they were asked to discuss and provided qualitative feedback for their scenario. In particular, 
they were asked to discuss which type of competitive advantage was relevant in the scenario. Participants
were encouraged to provide detailed feedback on their experiences and perceptions.
